---
title: "video_code_script"
format: html
editor: visual
---

```{r}
#install.packages("tidytuesdayR")
library(dplyr)
library(tidyr)
library(readr)

safi_data <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2023/2023-06-13/safi_data.csv')
```

```{r}
library(lubridate)

safi_data$year<-year(ymd(safi_data$interview_date))

data16<- safi_data|> filter(safi_data$year == 2016)
data16<- data16|>filter(!data16$key_ID == 1)

data17<- safi_data|> filter(safi_data$year == 2017)

```

```{r}

data16<-separate_longer_delim(data16, months_lack_food, delim = ";")

?separate_longer_delim()

data17<-separate_longer_delim(data17, months_lack_food, delim = ";")
```

```{r}

summary16<- data16|>group_by(village)|>
  summarise(n_months = n())|>
  ungroup()

summary17<- data17|> group_by(village)|>
  summarise(n_months = n())|>
  ungroup()

?inner_join

summaryall<- inner_join(summary16, summary17, by = "village")

```

```{r}
library(ggplot2)
library(ggpubr)

data16<-data16|>group_by(key_ID, village)

ggplot(data = data16, aes(x = months_lack_food, fill = village))+
  geom_bar(stat = "count", position = "dodge")+
  theme_pubr()+
  labs(title = "The Number of Households Without Food by Month")+
  labs(x = "Months without Food", y = "Count of Montsh")+
  scale_y_continuous(expand = c(0,0), limits = c(0,35))

ggplot(data = data17, aes(x = months_lack_food, fill = village))+
  geom_bar(stat = "count", position = "dodge")+
  theme_pubr()+
  labs(title = "The Number of Households Without Food by Month")+
  labs(x = "Months without Food", y = "Count of Montsh")+
  scale_y_continuous(expand = c(0,0), limits = c(0,25))


```

```{r}

safi_data <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2023/2023-06-13/safi_data.csv')


safi_data<- safi_data|>filter(!safi_data$key_ID == 1)
safi_data<- safi_data|>filter(!safi_data$memb_assoc == 'NULL')

safi_memb<- safi_data|>group_by(village)|>
  mutate(percent_members = mean(memb_assoc == 'yes')*100)

safi_nonmemb<- safi_data|>group_by(village)|>
  mutate(percent_nonmembers = mean(memb_assoc == 'no')*100)

percent_df<- bind_cols(safi_memb,safi_nonmemb['percent_nonmembers'])


```

```{r}

ggplot(percent_df, aes(x = village))+
  geom_bar(aes(y= percent_members, fill = "percent_members")stat = "identity", position = "dodge")+
  geom_bar(aes(y= percent_nonmembers, fill = "percent_nonmembers")stat = "identity", position = "dodge")
```

#The error that I did not figure out on camera was that I was missing a comma before using stat = "identity"

#geom_bar(aes(y= percent_members, fill = "percent_members"),stat = "identity", position = "dodge")

#\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_#

Time Index of 4 Techniques

Technique 1: Dates and Times using lubridate (6:20)

Technique 2: Tidyr-\> separate_longer_delim(13:00), group_by(17:30, 25:30, 39:00)

Technique 3: Dplyr-\> filter (7:40, 36:25), summarise (18:00), inner-join(22:40), mutate(39:50), bind_cols(43:00)

Technique 4: ggplot (22:55, 47:00)
